Robust Quantum Optimal Control

### 2020-07-23 paper/paper.tex
small update

%% F4.1
%% TODO: Update images. Use new gates constructed with
%% spline T1 and use smaller sim times.
\begin{figure*}[ht]
  \begin{subfigure}{.3\linewidth}
    \includegraphics[width=\linewidth]{assets/00045_spin16.png}
    \label{fig:sub-first}
  \end{subfigure}
  \begin{subfigure}{.3\linewidth}
    \includegraphics[width=\linewidth]{assets/00047_spin16.png}
    \label{fig:sub-second}
  \end{subfigure}
  \begin{subfigure}{.3\linewidth}
    \includegraphics[width=\linewidth]{assets/00049_spin16.png}
    \label{fig:sub-third}
  \end{subfigure}
  \caption{Master equation simulation with $T_{1}$ dissipation for all basis gates,
    comparing the performance of the analytic gates and the $T_{1}$ optimized QOC gates.}
  \label{fig:fig}
\end{figure*}

@@

%% S4
\section{Robustness to $T_{1}$-type Noise}
(Strategy) We seek to minimize the probability
that the qubit decays as a result of longitudinal
relaxation. To this end we add the
longitudinal relaxation probability
to the augmented state vector
\begin{equation}
  P_{1}(t) = \int_{0}^{t} \gamma_{1}(a(t^{\prime})) dt^{\prime}
\end{equation}
where $\gamma_{1} = T_{1}^{-1}$. Setting the target
longitudinal relaxation probability to 0 results in
a quadratic cost at each knot point
of the form ${\lvert P_{1}(t_{k}) \rvert}^{2}$.

@@

  \begin{subfigure}{\linewidth}
    \includegraphics[width=\linewidth]{assets/00006_spin12_hpsweep.png}
    \label{fig:5.1:a}
  \end{subfigure}
  \caption{\centering Robustness to qubit frequency detuning for
    the (2, 4)-point sampling method, (2\textsuperscript{nd}, 3\textsuperscript{rd})
    order derivative method, and CORPSE pulses for the $R_{x}(\pi/2)$ gate.
    (a) Gate fidelity as a function of the qubit frequency detuning.
    (b) Gate fidelity at one standard deviation from the nominal qubit frequency
    as a function of time.
  }
\end{figure}

@@

%% S5
\section{Robustness to $T_{\phi}$-type Noise}
(Strategy) For the fluxonium, pure dephasing acts
along the flux axis. Low frequency 1/$f$ noise,
Johnson-Nyquist current noise present in the flux bias
lines, and temperature dependent gain fluctuations
may cause the flux amplitude to deviate from its
desired value by an amount $\delta a$. Additionally,
residual calibration errors and fluctuations may cause
the qubit frequency to deviate from its measured value
by an amount $\delta \omega_{q}$.

>>>>

%% F4.1
%% TODO: Update images. Use new gates constructed with
%% spline T1 and use smaller sim times.
\begin{figure*}[ht]
  \begin{subfigure}{.3\linewidth}
    \includegraphics[width=\linewidth]{assets/00045_spin16.png}
  \end{subfigure}
  \begin{subfigure}{.3\linewidth}
    \includegraphics[width=\linewidth]{assets/00047_spin16.png}
  \end{subfigure}
  \begin{subfigure}{.3\linewidth}
    \includegraphics[width=\linewidth]{assets/00049_spin16.png}
  \end{subfigure}
  \caption{Master equation simulation with $T_{1}$ dissipation for all basis gates,
    comparing the performance of the analytic gates and the $T_{1}$ optimized QOC gates.}
\end{figure*}

@@

%% S4
\section{Robustness to Longitudinal Relaxation}
(Strategy) We seek to minimize the probability
that the qubit decays as a result of longitudinal
relaxation. To this end we add the
longitudinal relaxation probability
to the augmented state vector
\begin{equation}
  P_{1}(t) = \int_{0}^{t} \gamma_{1}(a(t^{\prime})) dt^{\prime}
\end{equation}
where $\gamma_{1} = T_{1}^{-1}$. Setting the target
longitudinal relaxation probability to 0 results in
a quadratic cost at each knot point
of the form ${\lvert P_{1}(t_{k}) \rvert}^{2}$.

@@

  \begin{subfigure}{\linewidth}
    \includegraphics[width=\linewidth]{assets/00006_spin12_hpsweep.png}
    \label{fig:5.1:b}
  \end{subfigure}
  \caption{\centering Robustness to qubit frequency detuning for
    the (2, 4)-point sampling method, (2\textsuperscript{nd}, 3\textsuperscript{rd})
    order derivative method, and CORPSE pulses for the $R_{x}(\pi/2)$ gate.
    (a) Gate fidelity as a function of the qubit frequency detuning.
    (b) Gate fidelity at one standard deviation from the nominal qubit frequency
    as a function of time.
  }
\end{figure}

@@

%% S5
\section{Robustness to Pure Dephasing}
(Strategy) For the fluxonium, pure dephasing acts
along the flux axis. Low frequency 1/$f$ noise,
Johnson-Nyquist current noise present in the flux bias
lines, and temperature dependent gain fluctuations
may cause the flux amplitude to deviate from its
desired value by an amount $\delta a$. Additionally,
residual calibration errors and fluctuations may cause
the qubit frequency to deviate from its measured value
by an amount $\delta \omega_{q}$.
